\textbf{Seasonal Dynamics of Epiphytic Microbial Communities on Marine Macrophyte Surfaces}

### 2021-08-17 submission/manuscript.Rmd
Production done.

Seagrasses are know to form close relationships with microbial communities associated with the surfaces of leaves, roots and rhizomes [@Cucio2016; @Ugarelli2019; @Wang2020; @Ettinger2020; @Crump2018]. For different seagrass species a distinct microbial community from ambient seawater or bulk sediment has been reported, however no species specific communities have been found [@Cucio2016; @Ugarelli2019; @Crump2018]. It seems that seagrasses are selecting the associated microbial community but these microbes have not coevolved with their seagrass plant host. Similar to seagrasses, siphonous macroalgae of the genus *Caulerpa* are also closely associated with their microbial communities [@Aires2015; @Aires2013; @Morrissey2019; @Rizzo2016a; @Stabili2017]. While some studies have found similar culturable bacterial groups associated with the surface of a *Caulerpa* species from different geographic locations [@Stabili2017], other have reported large compositional differences that were mainly attributed to different host species of this genus, biogeography and nutrient levels [@Morrissey2019] again raising the question to which extent are associated communities host-specific.

>>>>

Seagrasses are known to form close relationships with microbial communities associated with the surfaces of leaves, roots and rhizomes [@Cucio2016; @Ugarelli2019; @Wang2020; @Ettinger2020; @Crump2018]. For different seagrass species a distinct microbial community from ambient seawater or bulk sediment has been reported, however no species specific communities have been found [@Cucio2016; @Ugarelli2019; @Crump2018]. It seems that seagrasses are selecting the associated microbial community but these microbes have not coevolved with their seagrass plant host. Similar to seagrasses, siphonous macroalgae of the genus *Caulerpa* are also closely associated with their microbial communities [@Aires2015; @Aires2013; @Morrissey2019; @Rizzo2016a; @Stabili2017]. While some studies have found similar culturable bacterial groups associated with the surface of a *Caulerpa* species from different geographic locations [@Stabili2017], other have reported large compositional differences that were mainly attributed to different host species of this genus, biogeography and nutrient levels [@Morrissey2019] again raising the question to which extent are associated communities host-specific.

### 2021-08-17 submission/manuscript.tex
Production done.

Seagrasses are know to form close relationships with microbial
communities associated with the surfaces of leaves, roots and rhizomes
(Cúcio et al., 2016; Crump et al., 2018; Ugarelli et al., 2019; Ettinger
and Eisen, 2020; Wang et al., 2020). For different seagrass species a
distinct microbial community from ambient seawater or bulk sediment has
been reported, however no species specific communities have been found
(Cúcio et al., 2016; Crump et al., 2018; Ugarelli et al., 2019). It
seems that seagrasses are selecting the associated microbial community
but these microbes have not coevolved with their seagrass plant host.
Similar to seagrasses, siphonous macroalgae of the genus \emph{Caulerpa}
are also closely associated with their microbial communities (Aires et
al., 2013, 2015; Rizzo et al., 2016b; Stabili et al., 2017; Morrissey et
al., 2019). While some studies have found similar culturable bacterial
groups associated with the surface of a \emph{Caulerpa} species from
different geographic locations (Stabili et al., 2017), other have
reported large compositional differences that were mainly attributed to
different host species of this genus, biogeography and nutrient levels
(Morrissey et al., 2019) again raising the question to which extent are
associated communities host-specific.

>>>>

Seagrasses are known to form close relationships with microbial
communities associated with the surfaces of leaves, roots and rhizomes
(Cúcio et al., 2016; Crump et al., 2018; Ugarelli et al., 2019; Ettinger
and Eisen, 2020; Wang et al., 2020). For different seagrass species a
distinct microbial community from ambient seawater or bulk sediment has
been reported, however no species specific communities have been found
(Cúcio et al., 2016; Crump et al., 2018; Ugarelli et al., 2019). It
seems that seagrasses are selecting the associated microbial community
but these microbes have not coevolved with their seagrass plant host.
Similar to seagrasses, siphonous macroalgae of the genus \emph{Caulerpa}
are also closely associated with their microbial communities (Aires et
al., 2013, 2015; Rizzo et al., 2016b; Stabili et al., 2017; Morrissey et
al., 2019). While some studies have found similar culturable bacterial
groups associated with the surface of a \emph{Caulerpa} species from
different geographic locations (Stabili et al., 2017), other have
reported large compositional differences that were mainly attributed to
different host species of this genus, biogeography and nutrient levels
(Morrissey et al., 2019) again raising the question to which extent are
associated communities host-specific.
